---
title: "Lab6"
author: "Chao Fu & Michael Bailey"
data: "r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r }
library(bruteknapsack)
```
# Description
There are three functions to solve the knapsack problem, each function implements
a algorithm.

# Functions

## brute_force_knapsack()
1. The function implements the algorithm with complexity O(2^n). 
1. The return is an list with the biggest value and the items.

## dynamic_knapsack()
1. The function implements the dynamic programming algorithm. 
1. The return is an list with the biggest value and the items.

## greedy_knapsack()
1. The function implements the greedy algorithm. 
1. The return is an list with the biggest value and the items.

# Usage

## Install

```{r, eval=FALSE}
devtools::install_github("chafu696/Lab6")

```

## Example

```{r, eval=FALSE}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(w = sample(1:4000, size = n , replace = TRUE),
v = runif(n = n, 0 , 10000))
bfk <- brute_force_knapsack(x = knapsack_objects[1:8, ], W = 3500)
```
```{r, eval=FALSE}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(w = sample(1:4000, size = n , replace = TRUE),
v = runif(n = n, 0 , 10000))
bfk <- dynamic_knapsack(x = knapsack_objects[1:8, ], W = 3500)
```
```{r, eval=FALSE}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(w = sample(1:4000, size = n , replace = TRUE),
v = runif(n = n, 0 , 10000))
bfk <- greedy_knapsack(x = knapsack_objects[1:800, ], W = 3500)
```
